Inpainting with controlled frequency suppression in the Fourier domain

### 2011-06-24 project/Paper/paper.tex
Added plot of missing pixel error
Added comparison view Added images to the 'other_images' folder
Paper: Smaller captions.
Paper: Minor changes.

%\usepackage{times}
%\usepackage{balance}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{../plots/search_strategy_6.pdf}
\includegraphics[width=0.8\columnwidth]{../plots/search_strategy_2.pdf}
\caption{The threshold is optimized by iteratively.}
\label{threshold_optimization}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Baseline algorithms for various fractions of missing pixels.}
\label{baseline_algorithms}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{l|r|r}
Algorithm & Error & Deviation \\
\hline
Linear interpolation & ? & ? \\
Gaussian interpolation & ? & ? \\
Matching pursuit & ? & ? \\
\end{tabular}
\end{table}

Our algorithm did not perform equally well for all sample images: It worked best for ? (error ? and standard deviation ?) and worst for ? (error ? and standard deviation ?).

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/framing_artifacts.png}
\caption{Original image with mask (left) and its reconstruction (right).}
\label{edge_reconstruction}
\end{figure}

>>>>

\usepackage[font=footnotesize]{caption}

\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\columnwidth]{../plots/search_strategy_6.pdf}
\includegraphics[width=0.8\columnwidth]{../plots/search_strategy_2.pdf}
\caption{The threshold is iteratively optimized.}
\label{threshold_optimization}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/missingpixelsVsError.png}
\caption{Baseline algorithms for various fractions of missing pixels.}
\label{baseline_algorithms}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{l|c|c}
Algorithm & Error & Deviation \\
\hline
New algorithm & 5.73\e{-4} & 6.32\e{-6} \\
Linear interpolation & 8.08\e{-4} & 7.10\e{-6} \\
Gaussian interpolation & 5.74\e{-3} & 1.10\e{-5} \\
Matching pursuit & 1.72\e{-3} & 1.71\e{-5} \\
\end{tabular}
\end{table}

Our algorithm did not perform equally well for all sample images: It worked best for the spiral (error 1.25\e{-4} and standard deviation 1.92\e{-6}) and worst for the bicycles (error 3.05\e{-3} and standard deviation 4.09\e{-5}).

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{images/paper_reconstruction_bars32_mask8.png}
\caption{Original image with mask (left, mask in blue) and its reconstruction (right). Enlarged for display in this paper.}
\label{edge_reconstruction}
\end{figure}
